Reproducibility of SNP calling in multiple sequencing runs from single tumors

### 2015-04-17 PAPER/paper_d4.tex
more draft4 edits

We next looked at the individual effects of each of the five filters that we coded and one of the SomaticSniper filters (Variant Allele Quality, or VAQ). We first looked at the total number of putative SNPs removed by each filter (Figure 6). We found that different filters removed different numbers of mutations, and that the lion's share of mutations were removed by the VAQ and LOH filters, each of which removed 200 or more putative SNPs on average. Three other filters, those removing overlap with dbSNP and mutations within a 10 bp window of other mutations, also removed around 50--100 mutations each per sample (Figure 6). The final filter, which removed putative SNPs with less than 10\% coverage of the alternate allele, removed 0--1 putative SNPs on average, but did on occasion remove as many as 50.

>>>>

We next looked at the individual effects of each of the five filters that we coded and one of the SomaticSniper filters (Variant Allele Quality, or VAQ). We first looked at the total number of putative SNPs removed by each filter (Figure 6). We found that different filters removed different numbers of mutations, and that the lion's share of mutations were removed by the VAQ and LOH filters, which removed on average 309 (median=164, min=17, max=11,439, stdev=1,372) and 539 (median=169, min=3, max=8,538, stdev=1,051) putative SNPs, respectively. Three other filters, those removing overlap with dbSNP and mutations within a 10 bp window of indels or other SNPs, removed 16 (median=8, min=0, max=348, stdev=33), 28 (median=16, min=0, max=535, stdev=45), and 46 (median=19, min=0, max=1,515, stdev=115) putative mutations per sample (Figure 6). The final filter, which removed putative SNPs with less than 10\% coverage of the alternate allele, removed 1 putative SNP on average (median=1, min=1, max=36, sd=3).
